### 2016-03-17 manuscript.tex
Add figures and references

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2009}

@@

\section*{Introduction}
There are many methods for inferring the presence of admixture, e.g. methods using simple summary statistics detecting deviations from phylogenetic symmetry \cite{reich2009reconstructing} [Also cite patterson paper and paper from Monty's group] , methods estimating admixture proportions with programs such as Structure \cite{pritchard2000inference},  Admixture \cite{alexander2009fast} or RFmic [cite] [comment: we might want to make sure to add more citations here, for example all the ones from our previous papers and the ones from the ALDER paper.  People like to see themselves cited]. However, there has been less research on estimating admixture times, possibly because such methods require data which were unavailable until the advent of high-throughput next generation sequencing. Some recently developed methods use the inferred local ancestry of sequences to construct admixture tract length distributions [cite Pool&Nielsen, Gravel and yourself]. Over time, recombination is expected to decrease the average lengths of admixture tracts. The length distribution of admixture tracts is therefore informative about the time since admixture.  Much of the theory relating to tracts lengths is based on Fisher's famous theory of junctions \cite{fisher1949theory} and subsequent work by Stam \cite{stam1980distribution} and others [add as many citations here as possible]. For example, \cite{baird2003distribution} first discussed the length distribution of tracts descended from a single ancestor. These results informed later analyses of admixture tract length distribution, such as \cite{pool2009inference}, \cite{gravel2012population}, and \cite{liang2014lengths}. \cite{gravel2012population} also implemented the software program TRACTS, which estimates admixture histories by fitting the tract length distribution, obtained by local ancestry inference, to a exponential approximation.

@@

\section{Weighted Linkage Disequilibrium}
As \cite{loh2013inferring} noted, we cannot use the LD in the admixed population directly, because the allele frequency differences in the source populations can be of either sign. As in As \cite{loh2013inferring} , we solve this problem by computing the product of the values of the three-point linkage disequilibrium coefficient with the product of the allele frequency differences. Using equation \ref{local_ancestry} we obtain
$$
\left\delta_x\delta_y\delta_z D_3(d,d')\right=\delta_x^2\delta_y^2\delta_z^2\mathbb{E}[\text{cov}(A_x,A_y,A_z)],
$$
because the local ancestry in the admixed sample is independent of the allele frequencies in the admixed population. For inference purposes, we estimate this function by averaging over triples of SNPs which are separated by distances of approximately $d$ and $d'$. The LD term is estimated from the admixed population, while the $\delta$'s are estimated from reference populations which are closely related to the two source populations. We notice that both this approach, as well as the previous approaches (e.g., \cite{loh2013inferring} ), does not take genetic drift in the source populations after the time of admixture into account, i.e. there is an assumption of both this mehtod and previous methods that the allele frequencies in the ancestral source populations can be approximated well using the allele frequencies in the extant populations.

@@

\bibliographystyle{plos_template}
\bibliography{}

>>>>

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

@@

\section*{Introduction}
There are many methods for inferring the presence of admixture, e.g. methods using simple summary statistics detecting deviations from phylogenetic symmetry \cite{reich2009reconstructing} [Also cite patterson paper and paper from Monty's group] , methods estimating admixture proportions with programs such as Structure \cite{pritchard2000inference},  Admixture \cite{alexander2009fast} or RFmic [cite] [comment: we might want to make sure to add more citations here, for example all the ones from our previous papers and the ones from the ALDER paper.  People like to see themselves cited]. However, there has been less research on estimating admixture times, possibly because such methods require data which were unavailable until the advent of high-throughput next generation sequencing. Some recently developed methods use the inferred local ancestry of sequences to construct admixture tract length distributions [cite Pool Nielsen, Gravel and yourself]. Over time, recombination is expected to decrease the average lengths of admixture tracts. The length distribution of admixture tracts is therefore informative about the time since admixture.  Much of the theory relating to tracts lengths is based on Fisher's famous theory of junctions \cite{fisher1949theory} and subsequent work by Stam \cite{stam1980distribution} and others [add as many citations here as possible]. For example, \cite{baird2003distribution} first discussed the length distribution of tracts descended from a single ancestor. These results informed later analyses of admixture tract length distribution, such as \cite{pool2009inference}, \cite{gravel2012population}, and \cite{liang2014lengths}. \cite{gravel2012population} also implemented the software program TRACTS, which estimates admixture histories by fitting the tract length distribution, obtained by local ancestry inference, to a exponential approximation.

@@

\section{Weighted Linkage Disequilibrium}
As \cite{loh2013inferring} noted, we cannot use the LD in the admixed population directly, because the allele frequency differences in the source populations can be of either sign. As in As \cite{loh2013inferring} , we solve this problem by computing the product of the values of the three-point linkage disequilibrium coefficient with the product of the allele frequency differences. Using equation \ref{local_ancestry} we obtain
$$
\delta_x\delta_y\delta_z D_3(d,d')=\delta_x^2\delta_y^2\delta_z^2\mathbb{E}[\text{cov}(A_x,A_y,A_z)],
$$
because the local ancestry in the admixed sample is independent of the allele frequencies in the admixed population. For inference purposes, we estimate this function by averaging over triples of SNPs which are separated by distances of approximately $d$ and $d'$. The LD term is estimated from the admixed population, while the $\delta$'s are estimated from reference populations which are closely related to the two source populations. We notice that both this approach, as well as the previous approaches (e.g., \cite{loh2013inferring} ), does not take genetic drift in the source populations after the time of admixture into account, i.e. there is an assumption of both this mehtod and previous methods that the allele frequencies in the ancestral source populations can be approximated well using the allele frequencies in the extant populations.

@@

\bibliography{thesis}
